\documentclass[12pt, letterpaper, preprint, comicneue]{aastex63}
%\usepackage[default]{comicneue} % comic sans font for editing
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
\usepackage{xspace}
\usepackage{paralist}

% typesetting shih
\linespread{1.08} % close to 10/13 spacing
\setlength{\parindent}{1.08\baselineskip} % Bringhurst
\setlength{\parskip}{0ex}
\let\oldbibliography\thebibliography % killin' me.
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\parskip}{0pt}%
  \setlength{\bibsep}{0ex}
  \raggedright
}
\setlength{\footnotesep}{0ex} % seriously?

% citation alias

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}
\newcommand{\lss}{{\small{LSS}}\xspace}

\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{{\rm Mpc}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}

\let\oldAA\AA
\renewcommand{\AA}{\text{\normalfont\oldAA}}
% cmds for this paper 
\newcommand{\gr}{g{-}r}
\newcommand{\fnuv}{FUV{-}NUV}
\newcommand{\sfr}{{\rm SFR}}
\newcommand{\ssfr}{{\rm SSFR}}
\newcommand{\xobs}{\bfi{x}_{\rm obs}}
\newcommand{\btheta}{\boldsymbol{\theta}}
\newcommand{\bphi}{\boldsymbol{\phi}}
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\opcit}{\foreign{Op.~cit.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

\newcommand{\sedflow}{{\sc SEDflow}}
%% collaborating
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\definecolor{orange}{rgb}{1,0.5,0}
\newcommand{\chedit}[1]{{\color{orange}#1}}
\newcommand{\peter}[1]{{\color{red}#1}}

\begin{document} \sloppy\sloppypar\frenchspacing 

\title{Accelerated Bayesian SED Modeling using Amortized Neural Posterior Estimation}

\newcounter{affilcounter}
\author[0000-0003-1197-0902]{ChangHoon Hahn}
\altaffiliation{changhoon.hahn@princeton.edu.com}
\affil{Department of Astrophysical Sciences, Princeton University, Princeton NJ 08544, USA} 

\author[0000-0002-8873-5065]{Peter Melchior}
\affil{Department of Astrophysical Sciences, Princeton University, Princeton NJ 08544, USA} 
\affil{Center for Statistics and Machine Learning, Princeton University, 
Princeton, NJ 08544, USA}

\begin{abstract}
    State-of-the-art spectral energy distribution (SED) analyses use a
    Bayesian framework to infer the physical properties of galaxies from
    observed photometry or spectra.
    They require sampling from a high dimensional space of SED model parameters
    and take >$10-100$ CPU hours per galaxy, which renders them practically
    infeasible for analyzing the {\em billions} of galaxies that will be
    observed by upcoming galaxy surveys
    (\eg~DESI, PFS, Rubin, James Webb, and Roman). 
    In this work, we present an alternative scalable approach for
    rigorous Bayesian inference using Amortized Neural Posterior
    Estimation (ANPE). 
    ANPE is a simulation-based inference method that exploits neural network
    models to estimate the posterior probability distribution over the full
    range of observations.
    It requires no additional model evaluations to estimate the posterior after
    training. 
    To demonstrate the advantages of an ANPE approach, we present \sedflow, an
    SED modeling method that uses ANPE with the recent~\cite{hahn2022}~SED model,
    and apply it to optical photometry. 
    Once trained, deriving the posterior of galaxy properties with 
    \sedflow~takes \emph{${\sim}1$ second per galaxy}. 
    We validate \sedflow~using posteriors derived from standard
    Markov Chain Monte Carlo (MCMC) sampling and synthetic observations, with
    known true parameter values.  
    The \sedflow~posteriors are in excellent agreement with both the MCMC
    estimates and the true posteriors. 
    %We therefore conclude that using ANPE we derive accurate posteriors $>10,000\times$ faster than standard SED modeling methods. 
    Lastly, we apply \sedflow~to 33,883 galaxies in the NASA-Sloan Atlas and
    publicly release their posteriors.
\end{abstract}
\keywords{galaxies: evolution -- galaxies: statistics}

\input{intro}
\input{sbi}
\input{sedflow}
\input{obs}
\input{results}
\input{discuss}
\input{summary}

\section*{Acknowledgements}
\peter{
It's a pleasure to thank 
    Adam Carnall, 
    Miles Cranmer, 
    Kartheik Iyer,
    Andy Goulding,
    Jenny E. Green,
    Uro{\u s}~Seljak,
    Michael A. Strauss, 
    ...
for valuable discussions and comments.}
This work was supported by the AI Accelerator program of the Schmidt Futures Foundation.

\appendix
\input{fail}
%\bibliographystyle{mnras}
\bibliography{sedflow} 
\end{document}
