\documentclass[12pt, letterpaper, preprint, comicneue]{aastex63}
%\usepackage[default]{comicneue} % comic sans font for editing
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage[normalem]{ulem} 
\usepackage{xspace}
\usepackage{paralist}


% typesetting shih
\linespread{1.08} % close to 10/13 spacing
\setlength{\parindent}{1.08\baselineskip} % Bringhurst
\setlength{\parskip}{0ex}
\let\oldbibliography\thebibliography % killin' me.
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\parskip}{0pt}%
  \setlength{\bibsep}{0ex}
  \raggedright
}
\setlength{\footnotesep}{0ex} % seriously?

% citation alias

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}
\newcommand{\lss}{{\small{LSS}}\xspace}

\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{{\rm Mpc}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}

\let\oldAA\AA
\renewcommand{\AA}{\text{\normalfont\oldAA}}
% cmds for this paper 
\newcommand{\gr}{g{-}r}
\newcommand{\fnuv}{FUV{-}NUV}
\newcommand{\sfr}{{\rm SFR}}
\newcommand{\ssfr}{{\rm SSFR}}
\newcommand{\xobs}{\bfi{x}_{\rm obs}}
\newcommand{\btheta}{\boldsymbol{\theta}}
\newcommand{\bphi}{\boldsymbol{\phi}}
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\opcit}{\foreign{Op.~cit.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

\newcommand{\github}{\href{https://github.com/changhoonhahn/SEDflow/}{\faGithub}}


\newcommand{\sedflow}{{\sc SEDflow}}
%% collaborating
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\definecolor{orange}{rgb}{1,0.5,0}
\newcommand{\chedit}[1]{{\color{orange}#1}}
\newcommand{\peter}[1]{{\color{red}#1}}

\begin{document} \sloppy\sloppypar\frenchspacing 

\title{Accelerated Bayesian SED Modeling using Amortized Neural Posterior Estimation}

\newcounter{affilcounter}
\author[0000-0003-1197-0902]{ChangHoon Hahn}
\altaffiliation{changhoon.hahn@princeton.edu.com}
\affil{Department of Astrophysical Sciences, Princeton University, Princeton NJ 08544, USA} 

\author[0000-0002-8873-5065]{Peter Melchior}
\affil{Department of Astrophysical Sciences, Princeton University, Princeton NJ 08544, USA} 
\affil{Center for Statistics and Machine Learning, Princeton University, 
Princeton, NJ 08544, USA}

\begin{abstract}
    State-of-the-art spectral energy distribution (SED) analyses use a
    Bayesian framework to infer the physical properties of galaxies from
    observed photometry or spectra.
    They require sampling from a high-dimensional space of SED model parameters
    and take $>10-100$ CPU hours per galaxy, which renders them practically
    infeasible for analyzing the {\em billions} of galaxies that will be
    observed by upcoming galaxy surveys (\eg~DESI, PFS, Rubin, Webb, and Roman).
    In this work, we present an alternative scalable approach to 
    rigorous Bayesian inference using Amortized Neural Posterior
    Estimation (ANPE). 
    ANPE is a simulation-based inference method that employs neural networks
    to estimate the posterior probability distribution over the full
    range of observations.
    Once trained, it requires no additional model evaluations to estimate the
    posterior.  
    We present, and publicly release, \sedflow, an ANPE method to produce
    posteriors of the recent \cite{hahn2022} SED model from optical
    photometry.
    \sedflow~takes \emph{${\sim}1$ second per galaxy} to obtain the posterior
    distributions of 12 model parameters, all of which are in excellent
    agreement with traditional Markov Chain Monte Carlo sampling results.
    We also apply \sedflow~to 33,884 galaxies in the NASA-Sloan Atlas and
    publicly release their posteriors.
    \github
\end{abstract}
\keywords{galaxies: evolution -- galaxies: statistics}

\input{intro}
\input{sbi}
\pagebreak
\input{sedflow}
\input{obs}
\input{results}
\input{discuss}
\input{summary}

\section*{Acknowledgements}
It's a pleasure to thank 
    Adam Carnall, 
    Miles Cranmer, 
    Kartheik Iyer,
    Andy Goulding,
    Jenny E. Green,
    Jiaxuan Li, 
    Uro{\u s}~Seljak,
    and 
    Michael A. Strauss
for valuable discussions and comments.
This work was supported by the AI Accelerator program of the Schmidt Futures Foundation.

\appendix
\input{fail}
%\bibliographystyle{mnras}
\bibliography{sedflow} 
\end{document}
