\section{NASA-Sloan Atlas} \label{sec:obs}
As a demonstration of its speed and accuracy, we apply \sedflow~to optical
photometry from the NASA-Sloan Atlas\footnote{\url{http://nsatlas.org/}} (NSA).
The NSA catalog is a re-reduction of SDSS DR8~\citep{aihara2011} that includes
an improved background subtraction~\citep{blanton2011}.
We use SDSS photometry in the $u$, $g$, $r$, $i$, and $z$ bands, which are
corrected for galactic extinction using \cite{schlegel1998}.
To ensure that the galaxy sample is not contaminated, we impose a number of
additional quality cuts by excluding:
\begin{itemize}
    \item objects where the centroiding algorithm reports the
    position of the peak pixel in a given band as the centroid. 
    The SDSS photometric pipeline can struggle to accurately define the center
    of objects near the edge or at low signal-to-noise, so these cases are
    often spurious objects. 
    \item objects that have pixels that were not checked for peaks by the
    deblender. 
    \item objects where more than 20\% of point-spread function (PSF) flux is
    interpolated over as well as objects where the interpolation affected many
    pixels and the PSF flux error is inaccurate. 
    The SDSS pipeline interpolates over pixels classified as bad (\eg~cosmic
    ray).
    \item objects where the interpolated pixels fall within 3 pixels of their
    center and they contain a cosmic ray that was interpolated over.
    \item objects that were not detected at $\ge5\sigma$ in the original frame,
    that contain saturated pixels, or where their radial profile could not be
    extracted.
\end{itemize}
By excluding these objects, we avoid complications from artificats in the
photometry that we do not model. 
For additional details on the quality flags, we refer readers to the SDSS
documentation\footnote{\url{https://www.sdss.org/dr16/algorithms/flags_detail}}.
After the quality cuts, we have a total of 33,884 NSA galaxies in our sample.

% quality cuts that we impose 
% - not peak center: did not use brightest pixel as centroid; hint that an object may not be real
% - not notchecked: object contains pixels which were not checked for peaks by deblender; deblending may be unreliable
% - not PSF_FLUX_INTERP: more than 20% of PSF flux is interpolated over. May cause outliers in color-color plots, e.g.
% - BAD_COUNTS_ERROR: 	interpolation affected many pixels; PSF flux error is inaccurate and likely underestimated.
% - not both INTERP_CENTER and CR: 	interpolated pixel(s) within 3 pix of the center. Photometry may be affected. 	object contains cosmic rays which have been interpolated over; should not affect photometry
% - BINNED1: detected at ≥ 5σ in original imaging frame
% - not SATURATED: contains saturated pixels; affects star-galaxy separation
% - not NOPROFILE : 	only 0 or 1 entries for the radial flux profile; photometric quantities derived from profile are suspect

